### 2014-11-12 ThesisJo/derivations.tex
la2pdf commit - 2014:11:12	19:47:04	(Wed12.Nov)

Instead of solving the wave equation directly, we will make a qualified guess that the solution takes the form of a complex exponential:
%
\begin{align}
s(\p,t) &= A\,e^{j(\omega t - \k\dot\p)}
\end{align}
%

>>>>

Instead of solving the wave equation directly, we will make a qualified guess that the solution takes the form of a complex exponential in both time and space:
%
\begin{align}
s(\p,t) &= A\,e^{j(\omega t - \k\cdot\p)}
\end{align}
%
Inserting this into the wave equation yields:
%
\begin{align}
\nabla^2 s = \frac{\partial^2 s}{\partial x^2} + \frac{\partial^2 s}{\partial y^2} + \frac{\partial^2 s}{\partial z^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} \nn
\frac{\partial^2 s}{\partial x^2} + \frac{\partial^2 s}{\partial y^2} + \frac{\partial^2 s}{\partial z^2} &= \frac{1}{c^2}\frac{\partial^2 s}{\partial t^2} \nn
\end{align}
